% LaTeX source of my resume
% =========================

% See the `README.md` file for more info.
% This file is licensed under the CC-NC-ND Creative Commons license.

% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

\maintitle{Cedric Meury}{November 9, 1983}{Last update on \today}  % title on top of the document

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:cedric@meury.com}{cedric@meury.com}\sbull
\textsmaller{+}41 76 5800724\sbull
\href{http://www.cedric-meury.ch/}{www.cedric-meury.ch}\sbull
\href{http://ch.linkedin.com/pub/cedric-meury/29/65/b96/}{ch.linkedin.com/cedric-meury}
\\
Margarethenstrasse 84\sbull
4053 Basel\sbull
Switzerland

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Resourceful, enthusiastic and sociable geek with a long-time passion for computer science and information technology, a background in molecular biology and a knack for quality software.}
\\
\\
Learning from books I wrote my first QBasic application at the age of 13. Later I delved into Pascal, Perl, \acr{C} and \acr{C++}. My passion for software engineering was sparked.

To understand how nature tackles the engineering problem of encoding complex living things in DNA, I graduated in Molecular Biology in 2008. A minor in Computer Science was a natural choice.

After my graduation, the bioinformatics company Genedata hired me as a Test Engineer. My careful and thorough testing efforts in close collaboration with developers resulted in high quality releases.

To explore the quickly growing field of IT in pharmaceutical research I took on a position at the bio-tech company Actelion. I have enabled scientists to work efficiently by maintaining a diverse set of laboratory software. 

During this time, I was politicized by global events and started voluntary work for the Pirate Party in my spare-time. As elected president of the Pirates in Basel I strive to establish information policy as a topic in the local debate.

In 2011, I joined Netbreeze as a Software Engineer in the core development team. I contribute to the main product on the front- and back-end. The web application is closely tied to the fast moving and ever-growing world of social media. For a new feature, I have developed a prototype that stores data from a large data stream in the Solr indexing server.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://netbreeze.ch/}{Netbreeze GmbH}}
  {\textsc{D\"ubendorf, Switzerland}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {Software Engineer}
    {Aug \apo11 -- present}
    {\bodytext{Netbreeze helps companies and PR agencies observe and analyse online and social media. As part of the core development team I took over responsibility for parts of the back-end, operate the productive system on a cloud hosting provider and contribute to product development. I created a prototype that captures a big data stream and stores it in the Solr indexing server. My contributions to methodology are greatly valued, the team-chat facilitates communication between distributed team members and the new wiki software leads to quality documentation.}}
}

\headedsection
  {\href{http://www.actelion.com/}{Actelion Pharmaceuticals Ltd}}
  {\textsc{Allschwil, Switzerland}} {%
  \headedsubsection
    {\acr{IT} Onsite Support Analyst Drug Discovery}
    {Jan \apo10 -- Feb \apo11}
    {\bodytext{Actelion is a internationally operating bio-tech company featuring a large research facility in Allschwil. I served as the interface between the pharmaceutical research staff and corporate \acr{IT} and maintained a broad set of Scientific software. When a managed client was rolled out company-wide, I ensured a high acceptance rate in the demanding environment by careful scheduling of migrations and replacing incompatible legacy software with newer versions or alternatives.}}
}

\headedsection
  {\href{http://www.genedata.com/}{Genedata AG}}
  {\textsc{Basel, Switzerland}} {%
  \headedsubsection
    {Software Test Engineer}
    {Mar \apo08 -- Nov \apo09}
    {\bodytext{Genedata develops software that streamlines R\&D workflows and improves research productivity of pharmaceutical and biotechnology companies. I was responsible for ensuring quality assurance of a High-Throughput-Screening data analysis software. I planned, designed and performed functional, acceptance, confirmation and regression tests. As part of a Scrum team I excelled in diplomatic and tactful cooperation with the developers. I have developed a Java servlet based test management tool which has been in use ever since.}}
}

\headedsection
  {\href{http://www.imv.kiev.ua/}{Zabolotny Institute of Microbiology}}
  {\textsc{Kiev, Ukraine}} {%
  \headedsubsection
    {Trainee in Microbiology}
    {Aug \apo06 -- Sep \apo06}
    {\bodytext{During the two month traineeship coordinated by the {\href{http://www.iaeste.ch/}{IAESTE exchange program}} I worked at a microbiological laboratory and contributed to research on the effects of electromagnetical radiation on yeast.}}
}

\begin{center}
  \emph{Various part-time positions besides my studies and time in school are not listed here for brevity.} 
\end{center}


\spacedhrule{0.4em}{-0.4em}


\roottitle{Education}

\headedsection
  {\href{http://www.biozentrum.unibas.ch/}{Biozentrum}, \href{http://unibas.ch/}{University of Basel}}
  {\textsc{Basel, Switzerland}} {%
  \headedsubsection
    {Master of Science in Molecular Biology, Major in Cell Biology}
    {Oct \apo06 -- Mar \apo08}
    {\bodytext{Under the supervision of Dr. San Paolo and Prof. Keller I finished my studies with a master thesis about the influence of an \emph{E. coli} enzyme on protein translation efficiency (GPA 5.5/6). Lectures on Java programming and web technologies completed my education.}}
}

\clearpage

\roottitle{Training}

\headedsection
  {Stanford University Online Education (Coursera)}
  {\href{http://online.stanford.edu/courses}{online.stanford.edu}} {%
  \headedsubsection
    {Design and Analysis of Algorithms II (ongoing), Prof. Tim Roughgarden}
    {Jan \apo13}
    {\bodytext{Second part of the class covers advanced algorithm design principles such as the greedy and dynamic programming algorithm design paradigms, complexity classes and dealing with NP-complete problems.}}
}

\headedsection
  {BerkeleyX Online Education (edX)}
  {\href{https://www.edx.org/courses/BerkeleyX/CS169.1x/2013_Spring/about}{edx.org}} {%
  \headedsubsection
    {CS169.1x: Software as a Service (ongoing), Prof. David Patterson, Prof. Armando Fox}
    {Jan \apo13}
    {\bodytext{Fundamentals for engineering long-lasting software using Ruby on Rails. Design, development, testing, and public cloud deployment of a simple application using modern development techniques including behavior-driven design, user stories, test-driven development, velocity, and pair programming.}}
}

\headedsection
  {Stanford University Online Education (Coursera)}
  {\href{http://online.stanford.edu/courses}{online.stanford.edu}} {%
  \headedsubsection
    {Design and Analysis of Algorithms I, Prof. Tim Roughgarden}
    {Apr \apo12}
    {\bodytext{Introduction to algorithm design. Examples of covered topics are divide-and-conquer algorithms, master method, different sorting algorithms, breadth- and depth-first-search, Dijkstra, heaps, hash tables and balanced binary search trees.}}
}

\headedsection
  {Linux Professional Institute}
  {\href{https://www.lpi.org/linux-certifications/programs}{lpi.org}} {%
  \headedsubsection
    {Junior Level Linux Professional, LPIC-1}
    {Mar \apo10}
    {\bodytext{Well-grounded understanding of the Linux operating system, its setup, administration and daily use.}}
}

\headedsection
  {International Software Testing Qualifications Board}
  {\href{http://www.istqb.org/certification-path-root/foundation-level/foundation-level-content.html}{istqb.org}} {%
  \headedsubsection
    {ISTQB Certified Software Tester,  Foundation Level}
    {Apr \apo09}
    {\bodytext{Robust understanding of software testing, covering topics such as testing throughout the software life-cycle, static techniques, test design techniques, test management and tool support.}}
}

\headedsection
  {Sun Microsystems (previously)}
  {\href{http://education.oracle.com/}{education.oracle.com}} {%
  \headedsubsection
    {Sun Certified Java Programmer for the Java Platform, Standard Edition 6}
    {Aug \apo08}
    {\bodytext{Detailed knowledge of the core features and constructs of the Java programming language. It tests a wide range of Java's APIs and core features, starting from basics such as looping constructs and variables, to more complex topics such as Threads, Collections and Generics.}}
}

\spacedhrule{0.8em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Experience with:}
  {Java, Java EE (JPA, JMS, Servlet, Faces), Unit Testing, PostgreSQL, MySQL, Spring, Hibernate, Google Web Toolkit, Glassfish, Tomcat, Apache, Maven, Jenkins, Subversion, Git, Solr, Linux Server, Linux Desktop, Bash, Vagrant, AWS, DokuWiki, Scrum, Python, XML, Office Software, Twitter API, Facebook API}
\vspace{0.5em}
\inlineheadsection
  {Less experience with:}
  {GATE, Icinga, AWS, Ruby, Rails, BLAST, LaTeX, Perl, C, C++, PHP, GATE, Django}
\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {German \emph{(mother tongue)}, English \emph{(full professional proficiency; CAE, TOEFL 109/120)} and French \emph{(elementary proficiency)}.}

\spacedhrule{1.9em}{-0.4em}

\roottitle{Voluntary Work}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.piraten-basel.ch/}{Pirate Party Basel}}
  {\textsc{Basel, Switzerland}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {President}
    {Nov \apo10 -- present}
    {\bodytext{In my spare-time I helped establish the Pirate Party in Switzerland and took over a leading role in the regional chapter in Basel. I coordinate the work of the board, plan and participate in elections, represent the party in the media and collaborate with other sections and the national board. The efficient and enthusiastic work-force I built up managed to attract new activists and inspired many to engage in political issues.}}
}

\spacedhrule{1.1em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {Basel Fasnacht, enjoying music, gym, philosophy, politics, reading, science, strategic card games, supporting FC Basel}

\spacedhrule{1.8em}{-0.4em}

\roottitle{References}
\emph{Are available upon request.}
\end{document}
